Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-12-13 docs/00-manuscripts/ieee/ieee-manuscript.tex
discuss the lack of SWIR coverage

	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{above-ground biomass}
	\acro{ALE}{accumulated local effects}
	\acro{ALS}{airborne laser scanning}
	\acro{ANN}{artificial neural network}
	\acro{AUROC}{area under the receiver operating characteristics curve}
	\acro{BRT}{boosted regression trees}
	\acro{CART}{classification and regression trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{environmental niche modeling}
	\acro{FPR}{false positive rate}
	\acro{FFS}{forward feature selection}
	\acro{FS}{feature selection}
	\acro{GAM}{generalized additive model}
	\acro{GBM}{gradient boosting machine}
	\acro{GLM}{generalized linear model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{interquartile range}
	\acro{MARS}{multivariate adaptive regression splines}
	\acro{MBO}{model-based optimization}
	\acro{MEM}{maximum entropy model}
	\acro{ML}{machine learning}
	\acro{NDII}{normalized difference infrared index}
	\acro{NIR}{near-infrared}
	\acro{NRI}{normalized ratio index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{locally weighted scatter plot smoothing}
	\acro{PISR}{potential incoming solar radiation}
	\acro{PCA}{principal component analysis}
	\acro{PDP}{partial dependence plots}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{radial basis function}
	\acro{RF}{random forest}
	\acro{RMSE}{root mean square error}
	\acro{RR}{ridge regression}
	\acro{RSS}{residual sum of squares}
	\acro{SAR}{synthetic aperture radar}
	\acro{SDM}{species distribution modeling}
	\acro{SMBO}{sequential-based model optimization}
	\acro{SVM}{support vector machine}
	\acro{TPR}{true positive rate}
	\acro{VI}{vegetation index}
	\acro{XGBoost}{extreme gradient boosting}
\end{acronym}
\renewcommand{\IEEEiedlistdecl}{\relax}% reset back

@@

% \begin{figure} [t!]
% 	\begin{center}
% 		\centering
% 		\includegraphics[width=0.48\textwidth] {study-area-hyperspectral.pdf}
% 		\caption{Information about location, size and spatial distribution of trees for all plots used in this study.}\label{fig:study_area}
% 	\end{center}
% \end{figure}

@@

% Selected percentage of features across plots
% FIXME: Lösung einfügen nach Klärung mit Alex
Large differences were observed between the numbers of features selected during tuning for the subsequent fitting process.
Most features were selected during optimization when training without Laukiz2 and least when Laukiz1 served as the test set (\autoref{tab:tune-perc-sel-features}).
RF used only one feature when Luiando and Oiartzun served as the test data (0.00004 \% of 7675) while 34 and 230 features were seen as optimal during optimization when Laukiz1 and Laukiz2 were the test data, respectively.
In contrast, XGBoost and SVM used in all cases but Laukiz1 (less than 50 features; test set) more than two-thirds of all available features.

@@

The R package hsdar was used for the calculation of vegetation indices \cite{hsdar}.
All indices that could be calculated with the given spectral range of the data were used.
Even though this selection included a large number of available indices, some possibly relevant indices might have been missed by relying on the pre-selection of indices offered by the package.

@@

>>>>

	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{above-ground biomass}
	\acro{ALE}{accumulated local effects}
	\acro{ALS}{airborne laser scanning}
	\acro{ANN}{artificial neural network}
	\acro{AUROC}{area under the receiver operating characteristics curve}
	\acro{BRT}{boosted regression trees}
	\acro{CART}{classification and regression trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{environmental niche modeling}
	\acro{FPR}{false positive rate}
	\acro{FFS}{forward feature selection}
	\acro{FS}{feature selection}
	\acro{GAM}{generalized additive model}
	\acro{GBM}{gradient boosting machine}
	\acro{GLM}{generalized linear model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{interquartile range}
	\acro{MARS}{multivariate adaptive regression splines}
	\acro{MBO}{model-based optimization}
	\acro{MEM}{maximum entropy model}
	\acro{ML}{machine learning}
	\acro{NDII}{normalized difference infrared index}
	\acro{NIR}{near-infrared}
	\acro{NRI}{normalized ratio index}
	\acro{NDMI}{normalized difference moisture index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{locally weighted scatter plot smoothing}
	\acro{PISR}{potential incoming solar radiation}
	\acro{PCA}{principal component analysis}
	\acro{PDP}{partial dependence plots}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{radial basis function}
	\acro{RF}{random forest}
	\acro{RMSE}{root mean square error}
	\acro{RR}{ridge regression}
	\acro{RSS}{residual sum of squares}
	\acro{SAR}{synthetic aperture radar}
	\acro{SDM}{species distribution modeling}
	\acro{SMBO}{sequential-based model optimization}
	\acro{SVM}{support vector machine}
	\acro{TPR}{true positive rate}
	\acro{VI}{vegetation index}
	\acro{XGBoost}{extreme gradient boosting}
\end{acronym}
\renewcommand{\IEEEiedlistdecl}{\relax}% reset back

@@

\begin{figure*} [ht!]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth] {study-area-hyperspectral.pdf}
		\caption{Information about location, size and spatial distribution of trees for all plots used in this study.}\label{fig:study_area}
	\end{center}
\end{figure*}

@@

% Selected percentage of features across plots
Large differences were observed between the numbers of features selected during tuning for the subsequent fitting process.
Most features were selected during optimization when training without Laukiz2 and least when Laukiz1 served as the test set (\autoref{tab:tune-perc-sel-features}).
RF used only one feature when Luiando and Oiartzun served as the test data (0.00004 \% of 7675) while 34 and 230 features were seen as optimal during optimization when Laukiz1 and Laukiz2 were the test data, respectively.
In contrast, XGBoost and SVM used in all cases but Laukiz1 (less than 50 features; test set) more than two-thirds of all available features.

@@

The available hyperspectral data covered a wavelength between 400 nm and 1000 nm.
Hence, the wavelength range of the shortwave infrared (SWIR) region is not covered in this study.
Given that this wavelength range is often used in forest health studies \cite{hais2019}, e.g. when calculating the \ac{NDMI} index \cite{gao1996}, this marks a clear limitation of the dataset at hand.

The R package hsdar was used for the calculation of vegetation indices \cite{lehnert2016}.
All indices that could be calculated with the given spectral range of the data (400 nm - 1000 nm) were used.
This means even though \autoref{tab:vegindices} lists all available indices of the package, not all listed indices were used in this study.
Even though this selection included a large number of indices, some possibly helpful indices might have been missed due to the restriction of the hyperspectral data.

@@

\label{tab:vegindices}
